The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-17 document/ms.tex
some discussion

\begin{figure*}[htbp]~\\
\begin{center}
\includegraphics[width=\textwidth]{../prediction/shape_kdes.pdf}
\end{center}
\caption{%
\dfmfiglabel{shape-kdes}}
\end{figure*}

@@

\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
orbiting M-dwarfs by combining results from radial velocity and microlensing
surveys.
In the range $10^3\unit{days}<P<10^4\unit{days}$ and
$10\,M_\oplus<M<10^4\,M_\oplus$, they find a mean occurrence rate density
of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M/M_\mathrm{J}\,\dd\ln P/\unit{yr}}
    &\lesssim& 0.026
\end{eqnarray}
per M-dwarf.
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

@@

We have developed a fully automated method to search for the transits and
eclipses of long-period companions in photometric time series.
Applying this method to a subset of the \kepler\ archival light curves, we
discovered XX astrophysical transits.
Of these discoveries, at least about YY are likely to be planetary in nature.
Combining this catalog of discoveries with a measurement of the completeness
of our search method, we place a constraint on the occurrence rate of
long-period exoplanets.

@@

\acknowledgments
It is a pleasure to thank
So Hattori,
Angie Wolfgang,
and
Hans-Walter Rix
for helpful contributions to the ideas and code presented here.

>>>>

\begin{figure*}[htbp]~\\
\begin{center}
\includegraphics[width=\textwidth]{../prediction/shape_kdes.pdf}
\end{center}
\caption{%
Predicted eclipse shape distributions for the two false positive scenerios and
exoplanet transits (grayscale heatmap).
In this figure, the relative normalization of the maps are arbitrary but the
actual normalizations are given in the text.
The green points show the shapes parameters of the long-period exoplanet
candidates from Table~\ref{tab:catalog}.
\dfmfiglabel{shape-kdes}}
\end{figure*}

@@

\citet{Clanton:2014} studied the occurrence rate of long-period giant planets
orbiting M-dwarfs by combining results from radial velocity and microlensing
surveys.
In the period and mass range $10^3-10^4\unit{days}$ and $10-10^4\,M_\oplus$,
they find a mean occurrence rate density of
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M/M_\mathrm{J}\,\dd\ln P/\unit{yr}}
    &\lesssim& 0.026
\end{eqnarray}
per M-dwarf.
This result is slightly lower than our estimated rate for a similar range of
masses and periods but around G/K dwarfs.
This difference is consistent with previous results that cooler stars host
fewer long-period giant planets \citep[for example][]{Cumming:2008}.

Recently, \citep{Bryan:2016} studied the frequency of long-period giant
planets in systems with inner hot-Jupiters based on long-baseline radial
velocity monitoring of these systems \citep{Knutson:2014}.
In this sample, the computed occurrence rate of long-period giant planets was
found to be
\begin{eqnarray}
\frac{\dd^2 N}{\dd\ln M\,\dd\ln a} &=& 0.125 \pm 0.012
\end{eqnarray}
in the range $1-20\,M_\mathrm{J}$ and $5-20\unit{au}$.
This result is about a factor of two larger than our estimate
(\eqalt{massocc}) once again suggesting that cold-Jupiters preferentially
occur in systems with inner planets.

@@

We have developed a fully automated method to search for the transits of
long-period exoplanets in the \kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K-dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
Simulations of the false positive population~--~the secondary eclipses of
binary systems and background eclipsing binaries~--~suggest that 13 of these
candidates have high probability of being planetary in nature.

We measure the empirical detection efficiency function of our search procedure
by injecting simulated transit signals into the target light curves and
measuring the recovery rate.
By combining the measured detection efficiency and the catalog of exoplanet
candidates, we estimate the integrated occurrence rate of exoplanets with
orbital periods in the range $2-25\unit{years}$ and radii in the range
$0.1-1\,R_\mathrm{J}$ to be \intocc\ planets per G/K-dwarf.

Of these discoveries, at least about YY are likely to be planetary in nature.
Combining this catalog of discoveries with a measurement of the completeness
of our search method, we place a constraint on the occurrence rate of
long-period exoplanets.

@@

\acknowledgments
It is a pleasure to thank
So Hattori,
Jeff Coughlin,
Angie Wolfgang,
and
Hans-Walter Rix
for helpful contributions to the ideas and code presented here.
